---
title: "Doors-Experiment 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plyr)
library(BayesFactor)
library(lmerTest)
library(MCMCpack)
library(lsr)
library(cowplot)
library(ggsignif)
library(ggthemes)
library(RColorBrewer)
```

## Experiment 3: 1 animal vs. 8 animals as within-subject design

This is the analysis for our second doors experiment, where children show increased motivation, i.e. search longer, if they can gain more information. In this first experiment, 49 children were asked to search for an animal by opening doors. Crucially, the animal never appears but we manipulated the number of possible animals the final animal could be, i.e. 1 vs. 8. The prediction is that finding out which of 8 animals it would be is more informative than knowing the animal from the start. Thus, children should search longer in the 8 animals condition.

## Demographics

Let's start with the demographics.

```{r}
#read in data
dexp3<-read.csv("exp3.csv")

#head of the data frame
head(dexp3)

#demographics
##gender
table(dexp3$gender)
##age in months
mean(na.omit(dexp3$age))
sd(na.omit(dexp3$age))
```

## Group comparisons

Next, we will compare the two groups based on the number of doors they opened.

```{r}
ttestBF(subset(dexp3, condition=="1-animal")$ndoors- 
        subset(dexp3, condition=="8-animals")$ndoors,
        nullInterval=c(-Inf,0))

cohensD(subset(dexp3, condition=="1-animal")$ndoors- 
        subset(dexp3, condition=="8-animals")$ndoors)

t.test(subset(dexp3, condition=="1-animal")$ndoors- 
       subset(dexp3, condition=="8-animals")$ndoors,
       nullInterval=c(-Inf,0), 
       var.equal = TRUE)

```

Now we compare the two groups based on the latency until they looked away.

```{r}
ttestBF(na.omit(subset(dexp3, condition=="1-animal")$latency)- 
        na.omit(subset(dexp3, condition=="8-animals")$latency),
        nullInterval=c(-Inf,0))

cohensD(na.omit(subset(dexp3, condition=="1-animal")$latency)- 
        na.omit(subset(dexp3, condition=="8-animals")$latency))

t.test(na.omit(subset(dexp3, condition=="1-animal")$latency)- 
       na.omit(subset(dexp3, condition=="8-animals")$latency),
       nullInterval=c(-Inf,0), 
       var.equal = TRUE)

```
We also check the number of children who played the game until they were stopped.

```{r}
mfreq<-glmer(completion~condition+(1|id), family='binomial', data=dexp3)
summary(mfreq)

#mb0<-brm(completion~1+(condition|id), family='bernoulli', data=dexp3, save_all_pars = TRUE)
#mb1<-brm(completion~condition+(condition|id), family='bernoulli', data=dexp3, save_all_pars = TRUE)
#bayes_factor(mb1, mb0)
#Bayes Factor of this 125
```

Finally, we are also testing for differences when controlling for age.

```{r}
m<-MCMCregress(ndoors~age+condition, data=dexp3)
summary(m)
```


## Plotting

Finally, let's do some plotting. We begin by setting up some basic plotting functions.

```{r}
#standard errors
se<-function(x){sd(x)/sqrt(length(x))}

#data summary function
data_summary <- function(x) {
  m <- mean(x, na.rm=TRUE)
  sem <-sd(x, na.rm=TRUE)/sqrt(sum(!is.na(x)))
  ymin<-m-1.96*sem
  ymax<-m+1.96*sem
  return(c(y=m,ymin=ymin,ymax=ymax))
}

#position dodge
pd<-position_dodge(0.1)

#my palette
mypalette<-brewer.pal(7,"Dark2")
```

```{r}
#standard errors
se<-function(x){sd(x)/sqrt(length(x))}

#data summary function
data_summary <- function(x) {
  m <- mean(x, na.rm=TRUE)
  sem <-sd(x, na.rm=TRUE)/sqrt(sum(!is.na(x)))
  ymin<-m-1.96*sem
  ymax<-m+1.96*sem
  return(c(y=m,ymin=ymin,ymax=ymax))
}

#binomial function
mybinomfunc<-function(x, mark){
  b1<-binom.test(sum(x==mark), length(x), p=1/2, conf.level=0.95)
  dout<-data.frame(state=mark, p=as.numeric(b1$estimate), clow=b1$conf.int[1], cup=b1$conf.int[2])
  return(dout)
}

#position dodge
pd1<-position_dodge(0.1)
pd2<-position_dodge(0.01)

#my palette
mypalette<-brewer.pal(2,"Dark2")
```


```{r}
#point data frame
dpoint<-data.frame(Condition=dexp3$condition, doors=dexp3$ndoors)

#mark conditions
dpoint$Condition<-factor(dpoint$Condition, levels=c("1-animal", "8-animals"))

#summarized points
dm<-ddply(dpoint, ~Condition, summarize, m=mean(doors), se=se(doors))

#reshape summary data frame
dsum<-data.frame(m=dm$m,Conditionl=dm$Condition,ymin=dm$m-dm$se, ymax=dm$m+dm$se)

#let's plot it
p1<-ggplot(dpoint, aes(x =Condition, y = doors, fill=Condition, color=Condition))+
  #dot plots
  geom_dotplot(binaxis='y', stackdir='center',stackratio=1.5, dotsize=4, binwidth=0.5, position=pd1, alpha=0.5) +
  #summary function
  stat_summary(fun.data=data_summary, color="grey30", size=1, alpha=0.75)+
  #minimal theme
  theme_minimal()+ 
  #change text
  theme(text = element_text(size=20,  family="sans"))+
  #colors and fill
  scale_fill_manual(values =mypalette)+
  scale_color_manual(values = mypalette)+
  #write Bayes Factor on top
  geom_signif(comparisons=list(c("1-animal", "8-animals")), annotations="BF=34.9",
              y_position = 40, tip_length = 0, vjust=-0.1, col="black", size=1.1, textsize=6) +
  #label axes
  xlab("Condition")+ylab("Doors opened")+
  #scale of ticks
  scale_y_continuous(breaks=c(0,10,20,30,40,50), limits = c(0,50))+
  #no legend
  theme(legend.position="none", strip.background=element_blank(), legend.key=element_rect(color=NA))+
  #title
  ggtitle("Persistence")+
  #various theme changes including reducing white space and adding axes
  theme(axis.line.x = element_line(color="grey20", size = 1),
        axis.line.y = element_line(color="grey20", size = 1))

p1
```

Next, we plot the effect of condition onto latency.

```{r}
#point data frame
dpoint<-data.frame(Condition=dexp3$condition, latency=dexp3$latency)

#mark conditions
dpoint$Condition<-factor(dpoint$Condition, levels=c("1-animal", "8-animals"))

#summarized points
dm<-ddply(dpoint, ~Condition, summarize, m=mean(latency), se=se(latency))

#reshape summary data frame
dsum<-data.frame(m=dm$m,Conditionl=dm$Condition,ymin=dm$m-dm$se, ymax=dm$m+dm$se)

p2<-ggplot(dpoint, aes(x =Condition, y = latency, fill=Condition, color=Condition))+
  #dot plot
  geom_dotplot(binaxis='y', stackdir='center',stackratio=2, dotsize=4, binwidth=2, position=pd2, alpha=0.5) +
  #limits
  ylim(c(0, 220))+
  #summary function
  stat_summary(fun.data=data_summary, color="grey30", size=1, alpha=0.75)+
  #theme and fonts
  theme_minimal()+ theme(text = element_text(size=20,  family="sans"))+
  #colors and fill
  scale_fill_manual(values =mypalette)+
  scale_color_manual(values = mypalette)+
  #add Bayes Factor on top
  geom_signif(comparisons=list(c("1-animal", "8-animals")), annotations="BF=13.0",
              y_position = 200, tip_length = 0, vjust=-0.1, col="black", size=1.1, textsize=6) +
  #label axes
  xlab("Condition")+ylab("Latency in s")+
  #no legend
  theme(legend.position="none", strip.background=element_blank(), legend.key=element_rect(color=NA))+
  #title
  ggtitle("First signs of leaving")+
  #various theme changes including reducing white space and adding axes
  theme(axis.line.x = element_line(color="grey20", size = 1),
        axis.line.y = element_line(color="grey20", size = 1))

p2

```

Finally, we plot the difference in completion rates.

```{r}
#subset of data
dc1<-subset(dexp3, condition=="1-animal")
dc2<-subset(dexp3, condition=="8-animals")

#apply binomial function
dp<-rbind(mybinomfunc(dc1$completion, 1), mybinomfunc(dc2$completion, 1))
#labels state
dp$state<-c("1-animal", "8-animals")

#let's plot it
p3 <- ggplot(dp, aes(y=p, x=as.factor(state), fill=as.factor(state))) +
  #summarize as a bar
  stat_summary(fun.y = mean, geom = "bar", position = "dodge", color='black', width=0.6) + 
  #points
  geom_point()+
  #error bars
  geom_errorbar(aes(ymin=clow, ymax=cup),color='black', width = .33, position=position_dodge((width=0.9))) +
  #label axes
  ylab("Proportion")+ xlab("Condition")+ 
  #theme and font change
  theme_minimal()+ theme(text = element_text(size=20,  family="sans"))+
  #change color
  scale_fill_manual(values = mypalette)+
  #now legend
  theme(strip.background=element_blank(), legend.key=element_rect(color=NA), legend.position="none")+
  guides(color=FALSE, shape=FALSE)+
  #add Bayes Factor above
  geom_signif(comparisons=list(c("1-animal", "8-animals")), annotations="BF=124.9",
              y_position = 0.91, tip_length = 0, vjust=-0.1, col="black", size=1.1, textsize=6) +
  #change y limits
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,1.05)) +
  #change title
  ggtitle("Completion")+
  #various theme changes including reducing white space and adding axes
  theme(axis.line.x = element_line(color="grey20", size = 1),
        axis.line.y = element_line(color="grey20", size = 1))
#show plot
p3
```
